Gait Segmentation Model for Rotation Time Series Collected by a Wearable Sensor using Machine Learning

### 2025-04-08 article_segmentation.qmd
Multiple updates on redaction.

@@

Bagged trees and Random forest

@@

Neural networks

: *to do*

>>>>

## Methologic contributions

@@

Bagged trees and Random forest [@kuhn2013applied]

@@

Neural networks [@varma2018]

: Neural Networks are deep learning models inspired by the human brain. They consist of interconnected nodes organized in layers which process the data by passing it from one layer to the next. The input data is transformed with non-linear functions, allowing the model to return a classification for each observation as output. The model contains two essential parameters: weights on each connection and biases on each node. It learns data pattern by adjusting these parameters during forward and backward propagation for each observation to mimimize a loss that represents the difference between real and predicted values. Most often, the loss used is the cross-entropy which is defined as followed for the observation $m$:

: $$
\square(m) = - \sum_{k=1}^K t_k(m) \text{log}(y_k(m))
$$ {#eq-crossentropy}

: with:

: - $t_k$ the ground truth.
: - $ny_k$ the classification probability.

: These models are complex and rely on a performant algorithm for the parameter update and an adapted activation function, as well as possible utilisation of batch normalization and regularization to find a model with a good complexity for the data. Tuning is done to find the best hyper-parameters such as the number of layers and nodes and the learning rate.
